---
title: "Shiny Fama French"
output: 
  html_notebook: default
---


```{r setup, include = FALSE}
install.packages("tidyverse")
install.packages("tidyquant")
install.packages("timetk")
install.packages("broom")
```

```{r}

library(tidyquant)
library(tidyverse)
library(timetk)
library(broom)

knitr::opts_chunk$set(message=FALSE, warning=FALSE)
```



```{r}
# The symbols vector holds our tickers. 
symbols <- c("SPY","EFA", "IJS", "EEM","AGG")

returns_tq <- 
  tq_get(symbols, 
         get = "stock.prices",
         from = "2013-01-01") %>% 
  select(symbol, date, adjusted) %>% 
  group_by(symbol) %>%
  tq_transmute(select     = adjusted, 
                 mutate_fun = periodReturn,
                 period = "daily",
                 col_rename = "return") %>% 
  spread(symbol, return)
```


### Importing and Wrangling the Fama French Factors


```{r}
factors_input <- "Global_5_Factors_Daily"

factors_address <- 
  paste("http://mba.tuck.dartmouth.edu/pages/faculty/ken.french/ftp/", 
        factors_input, "_CSV.zip", 
        sep="" )

factors_csv_name <- paste(factors_input, ".csv", sep="")

temp <- tempfile()

download.file(
  # location of file to be downloaded
  factors_address,
  # where we want R to store that file
  temp)

Global_5_Factors <- 
  read_csv(unz(temp, factors_csv_name), skip = 6 ) %>%
  rename(date = X1, MKT = `Mkt-RF`) %>%
  mutate(date = ymd(parse_date_time(date, "%Y%m%d")))%>%
  mutate_if(is.numeric, funs(. / 100))

tail(Global_5_Factors)

```


### Join our data

```{r}

data_joined <-
  returns_tq %>% 
  left_join(Global_5_Factors) %>% 
  na.omit()

data_joined_tidy <- 
  data_joined %>% 
  gather(asset, return, -date, -MKT, -SMB, -HML, -RMW, -CMA, -RF) %>% 
  select(date, asset, return, everything())
```

### Exploratory

```{r}
data_joined %>%
  # Try SMB, HML, MKT
  ggplot(aes(x = MKT, y = EEM)) +
  geom_point(color = "cornflowerblue")
```

```{r}
data_joined %>%
  # Try SMB, HML, MKT
  ggplot(aes(x = MKT, y = EEM)) +
  geom_point(color = "cornflowerblue") +
  geom_smooth(method = "lm", 
              formula = y~x, 
              color = "pink", 
              se = TRUE)
```

```{r}
data_joined %>% 
  ggplot(aes(x = EEM)) +
  geom_histogram(fill = "cornflowerblue", color = "pink", bins = 60)
```

```{r}
data_joined %>% 
  ggplot(aes(x = EEM)) +
  #geom_histogram(fill = "cornflowerblue", color = "pink", bins = 60) +
  geom_density(color = "pink")
```

```{r}
data_joined %>% 
ggplot(aes(sample = SPY)) +
  geom_qq(color = "cornflowerblue") 
```

```{r}
data_joined_tidy %>%
  # Try SMB, HML, MKT
  ggplot(aes(x = MKT, y = return, color = asset)) +
  geom_point() +
  facet_wrap(~asset)
```

```{r}
data_joined_tidy %>%
  # Try SMB, HML, MKT
  ggplot(aes(x = MKT, y = return, color = asset)) +
  geom_point() +
  geom_smooth(method = "lm", 
              formula = y~x, 
              color = "pink", 
              se = TRUE) +
  facet_wrap(~asset)
```

```{r}
data_joined_tidy %>% 
  ggplot(aes(x = return, fill = asset)) +
  geom_histogram(bins = 60) +
  facet_wrap(~asset)
```

```{r}
data_joined_tidy %>% 
  ggplot(aes(x = return, color = asset)) +
  geom_density() +
  facet_wrap(~asset)
```

```{r}
data_joined_tidy %>% 
  ggplot(aes(sample = return, color = asset)) +
  geom_qq() +
  facet_wrap(~asset)
```

### Modeling data

```{r}
one_asset <- 
  data_joined_tidy %>% 
  filter(asset == "SPY")
```

One group, one model

```{r}
one_asset %>% 
  do(model = 
       lm(return ~ MKT + SMB + HML, 
                data = .)) #%>% 
  #tidy(model, conf.int = T, conf.level = .95)
  # glance(model)
  # augment(model)
```

One group, many models

```{r}
one_asset %>% 
  nest(-asset) %>% 
  mutate(model1 = map(data, ~ lm(return ~ MKT, 
                data = .)),
         model3 = map(data, ~ lm(return ~ MKT + SMB + HML, 
                data = .)))
  


```


Many groups, many models - write out the equations

```{r}
by_asset <- 
  data_joined_tidy %>% 
  group_by(asset) %>% 
  nest()

by_asset %>% 
  mutate(model1 = map(data, ~ lm(return ~ MKT, 
                data = .)),
         model3 = map(data, ~ lm(return ~ MKT + SMB + HML, 
                data = .))) #%>% 
  # mutate(tidied_model1 = map(model1, tidy),
  #        tidied_model3 = map(model3, tidy))

```

Many groups, many models - turn equations into functions and map them -> funcitonal programming

```{r}
library(modelr)

one_factor_model <- function(df) {
  lm(return ~ MKT, data = df)
}

three_factor_model <- function(df) {
  lm(return ~ MKT + SMB + HML, data = df)
}

five_factor_model <- function(df) {
  lm(return ~ MKT + SMB + HML + RMW + CMA, data = df)
}

by_asset %>%
  mutate(one_factor_model = map(data, one_factor_model),
         three_factor_model= map(data, three_factor_model),
         five_factor_model = map(data, five_factor_model))
```

Arrange by r-squared (model ranking? if we trust r-squared)

```{r}
by_asset %>% 
  mutate(one_factor_model = map(data, one_factor_model)) %>% 
  mutate(glance = map(one_factor_model, glance)) %>% 
  unnest(glance, .drop = TRUE) %>% 
  arrange(r.squared) #%>% 
  # ggplot(aes(x= asset, y = r.squared, color = asset)) + 
  #   geom_point()
```

```{r}
by_asset %>% 
  mutate(one_factor_model = map(data, one_factor_model)) %>% 
  mutate(glance = map(one_factor_model, broom::glance)) %>% 
  unnest(glance)
```

Add predictions and residuals et al.

```{r}
by_asset %>% 
  mutate(one_factor_model = map(data, one_factor_model)) %>% 
  mutate(predict = map(one_factor_model, augment)) %>% 
  unnest(predict) #%>% 
  # group_by(asset) %>% 
  # mutate(date = data_joined$date) %>% 
  # select(date, asset, return, .fitted) %>% 
  # ggplot(aes(x = date)) +
  # geom_line(aes(y = return), color = "blue") +
  # geom_line(aes(y = .fitted), color = "red") +
  # facet_wrap(~asset)
```

Tidy, glance and augment all models

```{r}

by_asset %>%
  mutate(one_factor_model = map(data, one_factor_model),
         three_factor_model= map(data, three_factor_model),
         five_factor_model = map(data, five_factor_model)) %>% 
  mutate(tidied_one = map(one_factor_model, tidy),
         tidied_three = map(three_factor_model, tidy),
         tidied_five = map(five_factor_model, tidy)) %>% 
  mutate(glanced_one = map(one_factor_model, glance),
         glanced_three = map(three_factor_model, glance),
         glanced_five = map(five_factor_model, glance)) %>%
  mutate(augmented_one = map(one_factor_model, augment),
         augmented_three = map(three_factor_model, augment),
         augmented_five = map(five_factor_model, augment))
  # unnest any broomed column for viewing
  # unnest(glanced_five)
```

